Quantum Mechanical Many-body Problems with Machine Learning Algorithms

### 2019-03-19 doc/MachineLearning/article2.tex
update

In this work we discuss differences and similarities between
traditional many-body methods like variational and diffusion Monte
Carlo approaches and unsupervised machine learning methods based on
so-called Boltzmann machines. In particular we point to similarities
between Monte Carlo approaches with shadow wave functions and
restricted Boltzmann machines. We discuss their pros and cons and
apply the various algorithms to studies of quantum dots. These are
systems of interacting electrons confined to move in low-dimensional
regions. We show also that the results obtained with restricted Boltzmann machines are of the same quality as those obtained with traditional variational Monte Carlo approaches.

>>>>

In this work we discuss differences and similarities between
traditional many-body methods like variational and diffusion Monte
Carlo approaches and novel unsupervised machine learning methods. The
latter are based on so-called Boltzmann machines. In particular we
point to similarities between Monte Carlo approaches with shadow wave
functions and restricted Boltzmann machines. We discuss their pros and
cons and apply the various algorithms to studies of quantum
dots. These are systems of interacting electrons confined to move in
low-dimensional regions. For two interacting electrons only we have
analytic solutions for the eigenpairs, providing us the with ways to benchmark the quality of our numerical simulations.

We show
also that the results obtained with restricted Boltzmann machines are
of the same quality as those obtained with traditional variational
Monte Carlo approaches.
